---
title: "test-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{test-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning = FALSE, message = FALSE}

library(GrandCanyonSandbaR)
```

### Find the Nearest Upstream Gage to any riverMile
This function is critical in caluclating the lag time, or the time it takes flow to travel from
the nearest upstream gage to the location of your sandbar site
```{r}

riverMile = 167.3
getNearestUpstreamGage(riverMile, messages = TRUE)


```
### Calculate the Lagtime between any point in the canyon and the nearest upstream gage
once lag time is calculated, local hydrographs and flow patterns can be calculated for each site. (comming soon)
```{r}

out <- findLagtime(rivermile = 32.9, message = TRUE)
print(out)


```

### Plot an interactive Hydrograph
The interactivity is helpful for zooming in and looking at flow patterns, NOTE: this function uses
dygraphs which requires the discharge data to be in xts format
```{r}
data("SampleQ_xts_cfs")
 plotInteractiveHydrograph(Qdat = SampleQ_xts_cfs,
   title= "Colorado River Discharge at Lees Ferry",
   subtitle = "October 3rd 2014 - October 11th 2014")
 
```

### plot stage discharge relationships at one of the sandbar sites
This function takes the measured stage discharge data at each site from previous surveys
and fits a a generalized power law model then outputs the model for use in other ways..
```{r}

model <- fitGeneralizedPowerLawModel('0307R') # Assumes '0307R' is a valid site in SandbarSites


```

### Next we will estimate discharge at a specified site using the stage discharge model
we do this by generating a grid of equally spaced elevation increments and applying the model
to calculate the likely discharge with lower and upper bounds for discharge in CFS and CMS

```{r}


grid <- GenerateEquallySpacedStageDischarge(sitename = '2201R') # Assumes '2201R' is a valid site in SandbarSites
discharge_info <- find_Q_from_WSE('2201R', grid, 400.002) # Assumes '2201R' is a valid site and grid is defined
print(discharge_info)
```
